### 2017-01-14 conclusion.tex
Conclusion draft

>>>>

Irregularities occur most often close to the terminator.  This is likely due to the presence of a very large density gradient between high density solar illuminated plasma on the dayside and low density plasma on the nightside.  In addition, if a SuperDARN radar itself is positioned close to the terminator, it is observing the density gradient along its boresight.  If small-scale irregularity growth is directionally dependent, this is additionally the optimal orientation from which to observe the plasma structures, leading to increased echo occurrence.

In the polar caps, backscatter is often observed at nighttime even when background plasma density is low and propagation conditions are too poor for FAIs to be observed with HF radar.  This implies an additional source of nighttime plasma density that is not easily accounted for by models.  Frequent polar patches that propogate from the dayside to the nightside could be the source of this additional density.  The requirements for confirming this hypotheis will be detailed further in Section \ref{sec:futurework}.

Nighttime observations of FAIs is also higher with a positive IMF By component.  This could be due to the control that the By component over ionospheric convection patterns.  In a convectional two-cell convection pattern, the plasma flows antisunward from dayside to nightside across the terminator.  In this arrangement, the plasma flow, \(\vec{V}_E\), and the density gradient, \(\vec{G}\), are antiparallel, the least favorable orientation for GDI growth.  However, with a significant IMF By component, the orientation of the convection cells rotates such that plasma is no longer convects antisunward, creating a situation where GDI is more favorable and plasma structures can develop more readily.  Additionally, an IMF By component can contribute to the formation of polar patches by creating convection perturbations that separate high density patches from the daytime resevoir, as described in Section \ref{sec:lit_patches}.  In this way, the IMF By component may be indirectly responsible for the increased observation of backscatter.  If patch occurrence increases, it can contribute to the nighttime background density, as described above, which can improve propagation conditions so that FAIs can be observed by 
HF radars.

In addition to simply providing additional background density so nighttime propagation conditions are sufficient for the radar to observe FAIs, polar patches can contribute to plasma irregularity formation directly by providing background density gradients for GDI to be operational on.  This raises the important question of exactly how and where plasma structures form around polar patches.  Observations have long suggested there is asymmetry in plasma structuring surrounding polar patches, but the results presented in Chapter \ref{sec:paper2} suggest that production may also be anisotropic.  Asymmetry and anisotropy are independent such that the plasma structures can exhibit either of them independently or both or neither.

The plasma drift and wavevector directions influence the asymmetry that is observed surrounding polar patches.  The direction that the patch is drifting relative to its elongation direction impacts the orientations of \(\vec{G}\) and \(\vec{V}_E\) and controls the GDI growth rate.  This also creates the asymmetry between the different edges of the patch because as the gradient direction changes, the irregularity growth rate changes.  Additionally, linear theory predicts that irregularity growth is anisotropic, so the orientation of the patch relative to the radar can also impact the observed irregularities.
